%-------------------------
% Resume in Latex
% Author : Yasser Arafat
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/CodeDude19}{\Large Yasser Arafat}} & Email : \href{mailto:yasser.info.work@gmail.com}{yasser.info.work@gmail.com}\\
  \href{https://github.com/CodeDude19}{https://github.com/CodeDude19} & Mobile : +91-8876840474 \\
\end{tabular*}


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sikkim Manipal Institute of Technology}{Sikkim, India}
      {Bachelor of Computer Science,  GPA: 8.70}{Jul. 2017 -- Aug. 2021}
    \resumeSubheading
      {Maharishi Vidya Mandir}{Assam, India}
      {Higher Secondary Science,  GPA: 8.00}{Jun. 2015 -- Apr. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dell Technologies}{Bangalore, India}
      {Incoming Summer Intern}{May 2020 - July 2020}
      \resumeItemListStart
        \resumeItem{Software Development Engineer}
          {Incoming Summer Intern at Dell India in Software Development.}
      \resumeItemListEnd
      
    \resumeSubheading
      {SMIT D'CoderS Hackathon}{Sikkim, India}
      {Question Setter \& Mentor}{Feb 2020}
      \resumeItemListStart
        \resumeItem{Mentor}
          {Question Setter and Mentor in the SMIT D'CoderS Hackathon that was conducted in Sikkim Manipal Institute of Technology.}
    \resumeItemListEnd
    \resumeSubheading
      {D'CoderS Club}{Sikkim, India}
      {Programming Mentor}{Jul 2019 - Present}
      \resumeItemListStart
        \resumeItem{Mentor}
          {App Developement, Web Developement,Competitive Programming,C++ Standard Library}
      \resumeItemListEnd

    \resumeSubheading
      {Micro-Pro LLC}{Kolkata, India}
      {Android App Developer Intern}{Jun 2019 - Jul 2019}
      \resumeItemListStart
        \resumeItem{Android Application}
          {Created Car Rental App for Sikkim Area. Included Cloud Storage Functionalities \& Booking System. }
      \resumeItemListEnd

    \resumeSubheading
      {ICCAP}{Sikkim, India}
      {Student Volunteer}{Feb 2019}
      \resumeItemListStart
        \resumeItem{Event Management}
          {Student Volunteer at International Conference on Advanced Computational and Communication Paradigms(ICCAP).}
      \resumeItemListEnd

    \resumeSubheading
      {Competitive Coder,CodeChef}{India}
      {Competitive Coder}{Sep 2018 - Present}
      \resumeItemListStart
        \resumeItem{Coder}{3 Star Competitve Coder in Codechef Platform using STL C++.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}{C++ STL, Python, Dart \& Flutter, JS, Java, C#, GML.}
    \resumeSubItem{Databases}{MySQL, SQLite, MongoDB.}
    \resumeSubItem{App/Web Developement}{HTML, CSS, JavaScript, NodeJS,  Flutter, Android, Angular.}
 \resumeSubHeadingListEnd


%-------------------------------------------
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{NewSky Social Media}
      {A Full-Fledged Social Media Platform created using Flutter-Dart, Firebase and NodeJS for NewSky Inc - https://play.google.com/store/apps/details?id=com.newsky.newsky\linebreak
      project link - Github}
    \resumeSubItem{Feelo}
      {A Food Delivery Service and Home Stay Service App created using Flutter-Dart, Firebase and NodeJS for NewSky Inc - https://play.google.com/store/apps/details?id=com.newsky.feelo\linebreak
      project link - Github}
    \resumeSubItem{CarGo App}
      {Developed a Cab Booking System speciﬁcally for Sikkim Area in India.\linebreak
      project link - Github}
    \resumeSubItem{SMIT Tracker}
      {Developed a WebApp for Sikkim Manipal Institute to check the GPA and Performance of College Students using automated Scraping of Data.\linebreak
      project link - Github}
   \resumeSubItem{Product Recommendation Engine}
      {Created a Product Recommendation Engine for Dell Technologies ,based on User Browsing Activities captured using Ad-Services.\linebreak
      project link - Github}
   \resumeSubItem{Windows Optimizer}
      {Developed a Desktop Application for Windows Platform that Reduces Current RAM usage and CPU usage in real time by freeing Resourses based on Priority.\linebreak
      project link - Github}
    \resumeSubItem{Bounce}
      {Developed a Physics Based Single Player Bounce Game for Android and Windows Platform.\linebreak
      project link - Github}
  \resumeSubHeadingListEnd

%

%-----------Awards-----------------
\section{AWARDS}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dell Hack2Hire Hackthon Winner}{Dell Technologies}
      {Won the Hack2Hire Hackathon Conducted by Dell Technologies\linebreak
      in SMIT, India.}{Nov 2019}
    \resumeSubheading
      {Codechef Global Rank 885}{Codechef}
      {Competed in CodeChef Long Challenge June 2019 and placed a Global Rank of 885.}{Jun 2019}
    \resumeSubheading
      {Web-Dev Hackathon Winner}{TechAdrista}
      {Won Web Development Hackathon held in SMIT Techical Fest,TechAdrista.}{March 2019}
    \resumeSubheading
      {Coding Blocks Scholarship}{Coding Blocks}
      {Competed in Coding Block's APAT Test and won a Scholarship of 50\%.}{March 2019}
  \resumeSubHeadingListEnd

\end{document}
